---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.  -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MD_Crime

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to investigate the numbers and types of crimes in Maryland in 2020. 
There are 30,587 observations, which can be identified by unique incident ID. Besides incident ID, 
16 variables are included in the dataset, including Crime Name1, Crime Name2, Crime Name3, Crime Name4,
Victim, City, Place1, Place2, Dispatch Date, Dispatch Time, Start Date, Start Time, End Date, End Time. 
Crime Name1 illustrates the general categories of crimes: crime against person, crime against property 
and crime against society. Crime Name2 provides specific crime names, such as burglary, arson, 
assault, etc. Crime Name3 illustrates the subcategories of each specific crime. For example, it specifies 
the name of drugs (e.g, Marijuana) involves in the crime. 
Crime Name4 provides further details of some crimes, such as "possessing" the drug or "selling" the drug. 
Place1 specifies where the crime is taken place, such as street, Grocery/supermarket. Place2 provides 
details of some places, such as "in vehicle" for "street". 

With this dataset, we can explore the most common types of crimes in MD in 2020. Crime against property 
is the most common main category of crime. More specifically, Larceny, assault and damage property 
are the three most commons crimes among all 70 crime types. There are total reports of 19,578 crimes 
against property, 10,326 larceny, 3723 assault, and 2578 damage property. 
Apart from that, we can investigate the cities in MD with the most crime reported. Silver Spring 
has a total number of 10,615 crimes reported, which is 34.7% of all reported crimes. Gaithersburg has 
the second highest number of crimes, which is 4,501 and 14.7% of all crimes. 
We can also depict the area with the highest crime cases from a more holistic perspective by graphing 
crimes with longitude and latitude. Furthermore, we can compare the dispatch date of the police and 
the start date of the crime to examine the efficiency of the police. It turns out that the police always 
dispatch on the same date for all the crimes.


## Installation

The development version of MD_Crime is available from [GitHub] (https://github.com/Reed-Math241/pkgGrpp) with:

``` r
# install.packages("devtools")
devtools::install_github("Reed-Math241/pkgGrpp")
```
## Example


```{r example}
library(MD_Crime)
```




