---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.  -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MD_Crime

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to investigate the numbers and types of crimes in Maryland in 2020. 
There are XXX observations, which can be identified by unique incident ID. Besides incident ID, 
XX variables are included in the dataset, including XXXX. X represents the general categories of 
crimes: crime against person, crime against property, crime against society, not a crime, others. 
X represents the specific crime name, X specifies subcategories or provide details, and X supply further 
details of some crimes. 

With this dataset, we can explore the most common types of crimes in MD in 2020, which are XXX. 
Apart from that, we can investigate the cities in MD with the highest crime rates. We can also depict 
the area with the highest crime cases from a more holistic perspective by graphing crimes with longitude 
and latitude. Furthermore, we can compare the dispatch date of the police and the start time of the 
crime to examine the efficiency of the police. 


## Installation

The development version of XXX is available from [GitHub](https://github.com/orgs/Reed-Math241/teams/pkggrpp) with:

``` r
# install.packages("devtools")
devtools::install_github("Reed-Math241/pkggrpp")
```
## Example


```{r example}
library(pkgDemo)
```




